\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[usenames]{color}
\pagestyle{empty}
\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagestyle{empty}


% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

% END RESUME DEFINITIONS
\begin{document}

%Name
\contact{John A. Myrda}{\href{http://www.johnmyrda.com}{www.johnmyrda.com}}{\href{mailto:hello@johnmyrda.com}{hello@johnmyrda.com}}{\href{tel:7085071108}{(708) 507-1108}}

% Objective
%\header{Objective}

%\begin{body}
%	\vspace{14pt}
%	To get a job
%\end{body}

%\smallskip

% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{University of Illinois Urbana-Champaign} \hfill \emph{December 2012}{} \\
	\hspace{4ex} Bachelor of Science in Engineering Physics \\
	\hspace{4ex} Minor in Computer Science\\
\end{body}

%\smallskip

% Experience
\header{Experience}

\begin{body}
	\vspace{14pt}
	\textbf{UIUC Engineering IT}, \emph{Linux Working Group} \hfill \emph{Urbana, IL}\\
	\hfill \emph{Feb 2014 - August 2014}\\
	\vspace*{-16pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items 
		\item Provide user support for Linux issues in the College of Engineering.
		\item Identify legacy Linux systems and migrate them to a Linux distribution maintained by Engineering IT.
		\item Maintain and create internal and end user documentation for Engineering IT Linux distributions.
		\item Respond swiftly to issues in instructional labs that used Linux computers.
	\end{itemize}

%\smallskip

	\vspace{14pt}
	\textbf{UIUC Engineering IT}, \emph{Assistant IT Specialist} \hfill \emph{Urbana, IL}\\
	\hfill \emph{Jan 2013 - Feb 2014}\\
	\vspace*{-16pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items 
		\item Managed schedules and training of 10-12 employees of the Help Desk student staff.
		\item Acted as a point of escalation when Help Desk student staff could not resolve customer issues.
		\item Maintained and created internal and end user documentation relating to common technical tasks.
%		\item Something about networking and AD stuff maybe
		\item Created web based tools with PHP, MySQL, and JavaScript to simplify daily tasks.
	\end{itemize}
	
	\vspace{14pt}
	\textbf{Coordinated Science Laboratory}, \emph{Front Line IT Support} \hfill \emph{Urbana, IL}\\
	\hfill \emph{Oct 2010 - Dec 2012}\\
	\vspace*{-16pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Repaired and replaced damaged computer hardware for end users.
		\item Installed Cat6 wiring for servers and aided in transition from Centrex phones to VOIP communications.
	\end{itemize}

\end{body}

\smallskip

% Skills
\header{Skills}

\begin{body}
	\vspace{14pt}
	\textbf{Languages:}{} C, C{}\verb!++!, Python, Java, PHP, JavaScript, \LaTeX \\
	\textbf{Operating Systems:}{} Windows, Mac OS X, Linux\\
	\textbf{Other:}{} Basic electronics and circuitry, Arduino/TI Launchpad, Raspberry Pi\\
\end{body}

\smallskip


% Activites
\header{Activities}

\begin{body}
	\vspace{14pt}
	\textbf{Physics Van}, UIUC Sponsored Outreach Program \hfill{} \emph{Fall 2010 - 2012}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Performed educational and scientific assemblies for elementary and middle school students.
	\end{itemize}	
	\smallskip
	\textbf{Engineering Open House}, Exhibition of Student Engineering Projects \hfill{} \emph{Spring Semester 2010 \& 2012}\\
\end{body}


% Page 2: Projects
% \pagebreak

\header{Projects}
\begin{body}
	\vspace{14pt}
	%\emph{Full write-ups of these projects can be found on \href{http://www.johnmyrda.com}{johnmyrda.com}}\\
	%\vspace{10pt}
	
	%Facebook App Project
	\textbf{outPlan}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item A social application for finding out when friends are available to hang out.
		\item Uses Parse.com as a back-end and the Facebook API to access social data.		
		\item Web based and written in JavaScript, using Backbone.js and RequireJS.
		\item Still in progress. The current application can be found at \emph{\href{http://www.outplan.me}{www.outplan.me}}.
	\end{itemize}		

	%Easy Button Project
	\textbf{Speed Settlers Timer}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Transformed an Easy Button in to a countdown timer to be used with board games.
		\item Controlled an LCD display, read button presses, and played sound via interrupt driven C code.
		\item Designed and soldered the wiring and circuitry connecting the microcontroller to all other components.
	\end{itemize}
	
	%Piboy Project
	\textbf{Raspberry Pi Game Boy}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Replaced internals of Game Boy with Raspberry Pi (RPi) and circuitry to create miniature game console.
		\item Implemented circuitry and Python script for the RPi to make Game Boy power switch and red LED work.		
		\item Configured RPi to work comfortably with USB game controllers in order to play classic games.
	\end{itemize}
		
\end{body}
%End Projects

\end{document}
